Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-03-21 analysis2_manuscript.tex
clean up of Ben's edits

\section*{Abstract}
    \label{abstract}
    Selection is a fundamental evolutionary force that shapes patterns of genetic variation across species.
    However, simulations incorporating realistic selection along heterogeneous genomes in complex demographic histories
    is challenging, limiting our ability to benchmark statistical methods aimed at detecting selection and to explore theoretical predictions.
    \stdpopsim is a community-maintained simulation library that already provides an extensive catalog of
    species-specific population genetic models.
    Here we present a major extension to the \stdpopsim{} framework that enables simulation of various modes
    of selection, including background selection, selective sweeps,
    and arbitrary distributions of fitness effects (DFE) acting on annotated subsets of the genome (for instance, exons).
    This extension maintains \stdpopsim's core principles of reproducibility and accessibility while adding support
    for species-specific genomic annotations and published DFE estimates.
    We demonstrate the utility of this framework by benchmarking methods for demographic inference,
    DFE estimation, and selective sweep detection across several species and scenarios.
    Our results demonstrate the robustness of demographic inference methods to selection on linked sites,
    reveal the sensitivity of DFE-inference methods to model assumptions,
    and show how genomic features, like recombination rate and the density of functional sequence, influence power to detect selective sweeps.
    This extension to \stdpopsim{} provides a powerful, new resource for the population genetics community
    to explore the interplay between selection and other evolutionary forces in a reproducible, low-barrier framework.

\section*{Introduction}
    \label{introduction}
    % selection
    Selection is a fundamental force in evolution, shaping the
    genetic diversity of populations and driving the adaptation of
    species to their environments. The effects of selection
    on genetic variation are complex, and can be difficult to disentangle
    from other evolutionary processes such as mutation, recombination,
    and genetic drift \citep[e.g.,][]{gillespie1991causes}.
    For instance, changes in population size can lead to fluctuations
    in genetic diversity across a recombining chromosome
    that can mimic the effects of selection \citep{simonsen1995properties},
    and lead to spurious inferences about the strength and targets of genetic adaptation
    \citep{simonsen1995properties,akey2004population,nielsen2005genomic}.
    In turn, selection can confound our ability to infer demographic
    history from allele frequencies \citep{ewing2016consequences,schrider2016effects} and
    estimates of inverse coalescent rate \citep{schrider2016effects, johri2021impact, cousins2024accurate}.
    Thus, it is imperative to jointly account for the effects of selection
    and demography when inferring evolutionary history from genetic data \citep[e.g.,][]{sheehan2016deep,johri2020toward},
    yet the number of tools for doing so remain limited.

    % simulation
    To meet the growing need for the interpretation,
    analysis, and exploration of realistic and complex evolutionary models,
    the field of population genetics has increasingly turned to simulation.
    Simulation in population genetics has a long history
    including both backward-in-time coalescent simulations
    \citep{kingman1982genealogy,hudson1983testing, hudson1990gene}
    and forward-in-time simulations of complex demography and selection
    \citep[e.g.,][]{gillespie1984molecular, hernandez2008flexible, thornton2014c++, haller2019slim, gaynor2021AlphaSimR}.
    The development of simulation tools has been driven by the need to
    understand the effects of complex evolutionary processes on genetic
    variation \citep[e.g.,][]{peischl2013accumulation, thornton2019polygenic, galloway2020few, zhang2020impact},
     to provide a null model for hypothesis testing
    \citep[e.g.,][]{hudson1992statistical,hudson1994evidence,sabeti2002detecting},
    to explore the power and limitations of statistical methods \citep[e.g.,][]{przeworski2002signature, macleod2014effects},
    and increasingly to provide a basis for machine learning and other
    simulation-based inference methods
    \citep[e.g.,][]{beaumont2002approximate,lin2011distinguishing,kern2018diplos,mughal2019localizing,sanchez2021deep,wang2021automatic, zhang2023maladapt, smith2023dispersenn2}.
    However, joint simulation of complex demography and selection on realistic genomes is challenging,
    requiring many choices including the strength and rate of selection,
    and a parameterized demographic model,
    as well as implementation of genetic maps and other genomic features related to the strength of selection.
    This is a daunting task, and can be a barrier to
    the adoption of simulation-based methods in population genetics.
    Furthermore, different simulation and inference tools may use different structures
    and parameter scalings for their models,
    making it difficult to directly compare across these tools and the studies that use them.

    % stdpopsim
    In light of the complexities associated with estimating and simulating
    population genetic models, it is no surprise that
    a lingering challenge with simulation in population genetics has been
    reproducibility and the ability to share and compare results among
    researchers \citep[e.g.,][]{ragsdale2020lessons}.
    This challenge has been addressed in part by the development
    of community resources for sharing and distributing simulation software
    via the \stdpopsim project \citep{adrion2020community}. \stdpopsim
    provides a standardized interface for accessing a wide range of
    population genetic models, and has been widely adopted by the community
    \citep[e.g.,][]{speidel2021inferring, wang2021automatic, yang2022trustgwas, degiorgio2022spatially, browning2023fast, schweiger2023ultrafast, temple2024modeling, haag2025pandora}.
    Yet, previous releases of \stdpopsim did not include
    models of selection, which is a major limitation for more empirically motivated
    applications of population genetic simulation. In particular, modeling selection
    through simulation is critical for understanding processes such
    as adaptation \citep[e.g.][]{thornton2019polygenic,hartfield2024polygenic}, the effects of selective sweeps
    \citep[e.g.][]{braverman1995hitchhiking,fay2000hitchhiking,przeworski2002signature,przeworski2005signature,schrider2015soft},
    and the impact of background selection on genetic diversity
    \citep[e.g.][]{charlesworth1993effect,charlesworth1995pattern,williamson2002genealogy,ewing2016consequences,torres2020temporal}.
    Ideally, one would like
    to have a simple, unified framework for simulating both neutral and
    non-neutral evolutionary processes and to be able to compare the
    results of these simulations to empirical data in a manner that is
    both accessible to a wide range of researchers and highly reproducible.
    Furthermore, the framework should include the complex realities of
    genomes, including heterogeneous recombination rates,
    variation in the size and density of functional elements, and
    non-equilibrium demographic histories. Moreover, one should be able
    to model all of these features simultaneously using estimates and annotations obtained
    from a species of interest \citep[e.g.][]{schrider2020background,rodrigues2024shared}.
    %
    \stdpopsim{} provides a framework for such models,
    thus lowering the barrier to production of complex, multifaceted simulations,
    and allowing a wider range of researchers to make use of high-quality simulations
    in developing or testing their work.
    The project also holds as a central goal open, collaborative, and inclusive work,
    viewing capacity-building across the community as equal in importance to software development.

@@

    From a user's perspective, a model of selection is specified by pairing a \texttt{DFE} object
    with a collection of genomic segments defined using an \texttt{Annotation} object.
    Multiple such pairings can be defined in one simulation
    to provide a rich model of how selection may vary along a chromosome.
    For example, coding sequences may be associated with one DFE and non-coding sequences in exons with another DFE.
    Simulations with selection are then implemented by specifying a species,
    a portion of the genome to simulate,
    a genetic map if available, a model of demography, and pairings of DFEs with genomic segments
    using either the Python API or the command-line interface (Figure \ref{fig:schematic}B-C).
    Simulations with selection are generated
    using the \slim simulation engine, which is perhaps
    the most flexible simulation engine for modeling selection available to date
    (\msprime's selection models are relatively limited and thus not currently used by \stdpopsim).

@@

\section*{Discussion}
    \label{Discussion}
    In this paper, we have presented an important new addition to the \stdpopsim{} library
    that allows for simulating genetic variation in the presence of selection.
    We have demonstrated the utility of this new API by showing how it can be used to benchmark
    the performance of different methods for demographic history inference, the inference of the distribution
    of fitness effects of new mutations, and the detection of selective sweeps.
    This allows for a wide range of models of selection to be easily simulated and compared to
    empirical data, with reproducibility, computational efficiency, and rigor.

    The exploration of performance among methods done here is not meant to be thorough
    benchmarking, but rather to highlight the utility of the \stdpopsim resource.
    Having said that, there are a number of interesting results that bear discussion.
    The first pertains to estimation of demographic history ($N_e(t)$) in the context of
    linked purifying selection. Our simulations of humans and vaquita genomes
    model deleterious mutations only at exonic positions of the genome.
    As shown in Figures \ref{fig:homsap-summary-stats} and \ref{fig:vaquita-summary-stats},
    this combination only produces sizable decreases in polymorphism at exonic positions,
    which represent a small minority of sites within the genome, and does not lead to large-scale
    perturbations in genome-wide diversity. Thus, it is not surprising that estimates of $N_e(t)$
    from genome-wide data from which exons have been masked should be accurate
    (e.g., Figures \ref{fig:human-demography} and \ref{fig:vaquita-demography}).
    However, the question remains to what extent this would be true in empirical data where
    selection is not constrained to coding positions. For instance, we know
    that many genomes harbor large numbers
    of conserved non-coding elements \citep[e.g.,][]{siepel2005evolutionarily} with extremely
    strong selection acting on them \citep{katzman2007human,mclean2008dispensability}.
    We thus caution extrapolating from our results. Future studies might build upon
    the annotations we used here to include selection at other portions of the genome as well
    as mixtures of DFEs across sites.

    A second important finding is that inference of the DFE
    is sensitive to the dominance of deleterious mutations.
    All three of the DFE-inference methods applied here assume that deleterious mutations act
    in an additive fashion ($h=0.5$) by default.
    However, the simulated DFE for the vaquita genome included highly recessive mutations.
    Specifically, these simulations used a DFE where mutations with $s<-0.01$ are quite recessive,
    with $h<=0.01$, and where mutations with $-0.01<s<-0.001$ have $h=0.1$.
    We found that the three DFE-inference methods underestimated $E[s]$ and overestimated the shape parameter (Figure \ref{fig:vaquita-dfe}A-B).
    This performance is not surprising as decreasing $h$ for a given distribution of $s$ will lead to a decrease in $hs$,
    or an apparent decrease in the amount of selection.
    Fitting a mis-specified DFE that assumes $h=0.5$ will then lead to underestimates of $E[s]$.
    Indeed, the distribution of $hs$ is much more accurately estimated (Figure \ref{fig:vaquita-dfe}C).
    Overall, these results are consistent with prior work showing that it is challenging to separately
    infer the DFE of $s$ along with $h$ \citep{veeramah2014evidence, kyriazis2024constraining, balick2022overcoming}
    and that a large proportion ($>5\%$) of recessive deleterious mutations can confound inferences of $s$ \citep{wade2023quantifying}.
    Given the plethora of evidence for recessive deleterious mutations
    \citep{mukai1972mutation, agrawal2011inferences, huber2018gene, di2024revisiting},
    these results suggest the need for care in DFE inference.
    Kyriazis and Lohmueller \citeyear{kyriazis2024constraining} inferred the DFE of $s$ for nonsynonymous mutations
    in humans when considering different values of $h$.
    Intriguingly, additive models showed a satisfactory fit to the SFS of nonsynonymous variants in humans
    and more complex models of dominance did not substantially improve the fit.
    Nevertheless, models including recessive deleterious mutations, like those simulated here for the vaquita genome,
    show a similar fit to the SFS and may be more biologically realistic than fully additive models,
    given the evidence for the presence of recessive deleterious mutations.
    More broadly, new computational approaches are needed to precisely quantify the DFE and the covariance of $h$ and $s$.

    Further, inference of the DFE was done here using exon annotations of the genome in question.
    A key distinction between our analyses and those done in practice
    is that we have complete knowledge of which sites are under selection in the simulation,
    thus our inferences represent a best case scenario. Empirical inference of the DFE is a much
    harder problem as some mutations assumed to be free of selection
    may in reality be under selection and strength of selection can change over time or with environment.

    Regarding sweep detection, the inclusion of selection models into \stdpopsim allowed us to readily compare the
    effectiveness of different methods on data reflecting the demographic history, recombination rate variation,
    and genomic locations of negatively selected sites present in human populations. These results clearly demonstrate
    the impact of recombination rate variation, and underscore the importance of training methods on data with variable
    recombination rates \citep[e.g.,][]{schrider2017soft}. In addition, our results
    illustrate a strength of likelihood methods like \sweepfinder, that do not require a predefined window size.
    Window-based methods, such as \diploshic, tend to lag in performance when the genomic region affected by the sweep is
    larger than the chosen window size, as can occur with very strong sweeps or low levels of
    recombination. Moreover, while all the methods examined here retain adequate power for sweep identification across
    scenarios, including the inclusion of background selection, our results underscore the importance of developing
    methods that are well powered in the face of unknown demographic histories. Indeed, larger differences
    in power were observed when applying a method to genomes simulated with different demographic histories (i.e., YRI versus CEU)
    than when calibrating a method using a null model with and without background selection.

@@

\section*{Acknowledgments}\label{acknowledgements}
We thank Tom Booker for discussions and encouragement to incorporate realistic BGS models into \stdpopsim.
We thank the numerous users of the \stdpopsim package and well as
workshop participants who provided feedback and suggestions for improvements.

>>>>

\section*{Abstract}
    \label{abstract}
    Selection is a fundamental evolutionary force that shapes patterns of genetic variation across species.
    However, simulations incorporating realistic selection along heterogeneous genomes in complex demographic histories
    are challenging, limiting our ability to benchmark statistical methods aimed at detecting selection and to explore theoretical predictions.
    \stdpopsim is a community-maintained simulation library that already provides an extensive catalog of
    species-specific population genetic models.
    Here we present a major extension to the \stdpopsim{} framework that enables simulation of various modes
    of selection, including background selection, selective sweeps,
    and arbitrary distributions of fitness effects (DFE) acting on annotated subsets of the genome (for instance, exons).
    This extension maintains \stdpopsim's core principles of reproducibility and accessibility while adding support
    for species-specific genomic annotations and published DFE estimates.
    We demonstrate the utility of this framework by benchmarking methods for demographic inference,
    DFE estimation, and selective sweep detection across several species and scenarios.
    Our results demonstrate the robustness of demographic inference methods to selection on linked sites,
    reveal the sensitivity of DFE-inference methods to model assumptions,
    and show how genomic features, like recombination rate and functional sequence density, influence power to detect selective sweeps.
    This extension to \stdpopsim{} provides a powerful new resource for the population genetics community
    to explore the interplay between selection and other evolutionary forces in a reproducible, low-barrier framework.

\section*{Introduction}
    \label{introduction}
    % selection
    Selection is a fundamental force in evolution, shaping the
    genetic diversity of populations and driving the adaptation of
    species to their environments. The effects of selection
    on genetic variation are complex, and can be difficult to disentangle
    from other evolutionary processes such as mutation, recombination,
    and genetic drift \citep[e.g.,][]{gillespie1991causes}.
    For instance, changes in population size can lead to fluctuations
    in genetic diversity across a recombining chromosome
    that can mimic the effects of selection \citep{simonsen1995properties},
    leading to spurious inferences about the strength and targets of genetic adaptation
    \citep{simonsen1995properties,akey2004population,nielsen2005genomic}.
    In turn, selection can confound our ability to infer demographic
    history from allele frequencies \citep{ewing2016consequences,schrider2016effects} and
    estimates of inverse coalescent rate \citep{schrider2016effects, johri2021impact, cousins2024accurate}.
    Thus, it is imperative to jointly account for the effects of selection
    and demography when inferring evolutionary history from genetic data \citep[e.g.,][]{sheehan2016deep,johri2020toward},
    yet the number of tools for doing so remain limited.

    % simulation
    To meet the growing need for the interpretation,
    analysis, and exploration of realistic and complex evolutionary models,
    the field of population genetics has increasingly turned to simulation.
    Simulation in population genetics has a long history
    including both backward-in-time coalescent simulations
    \citep{kingman1982genealogy,hudson1983testing, hudson1990gene}
    and forward-in-time simulations of complex demography and selection
    \citep[e.g.,][]{gillespie1984molecular, hernandez2008flexible, thornton2014c++, haller2019slim, gaynor2021AlphaSimR}.
    The development of simulation tools has been driven by several needs:
    understanding the effects of complex evolutionary processes on genetic
    variation \citep[e.g.,][]{peischl2013accumulation, thornton2019polygenic, galloway2020few, zhang2020impact},
    obtaining a null model for hypothesis testing
    \citep[e.g.,][]{hudson1992statistical,hudson1994evidence,sabeti2002detecting},
    exploring the power and limitations of statistical methods \citep[e.g.,][]{przeworski2002signature, macleod2014effects},
    and increasingly, providing a basis for machine learning and other
    simulation-based inference methods
    \citep[e.g.,][]{beaumont2002approximate,lin2011distinguishing,kern2018diplos,mughal2019localizing,sanchez2021deep,wang2021automatic, zhang2023maladapt, smith2023dispersenn2}.
    However, joint simulation of complex demography and selection on realistic genomes is challenging,
    requiring many choices including the strength and rate of selection,
    and a parameterized demographic model,
    as well as implementation of genetic maps and other genomic features related to the strength of selection.
    This is a daunting task, and can be a barrier to
    the adoption of simulation-based methods in population genetics.
    Furthermore, different simulation and inference tools often use different structures
    and parameter scalings for their models,
    making it difficult to directly compare across these tools and the studies that use them.

    % stdpopsim
    In light of the complexities associated with estimating and simulating
    population genetic models, it is no surprise that
    a lingering challenge with simulation in population genetics has been
    reproducibility and the ability to share and compare results among
    researchers \citep[e.g.,][]{ragsdale2020lessons}.
    This challenge has been addressed in part by the development
    of community resources for sharing and distributing simulation software
    via the \stdpopsim project \citep{adrion2020community}. \stdpopsim
    provides a standardized interface for accessing a wide range of
    population genetic models, and has been widely adopted by the community
    \citep[e.g.,][]{speidel2021inferring, wang2021automatic, yang2022trustgwas, degiorgio2022spatially, browning2023fast, schweiger2023ultrafast, temple2024modeling, haag2025pandora}.
    Yet, previous releases of \stdpopsim did not include
    models of selection, which is a major limitation for more empirically motivated
    applications of population genetic simulation. In particular, modeling selection
    through simulation is critical for understanding processes such
    as adaptation \citep[e.g.][]{thornton2019polygenic,hartfield2024polygenic}, the effects of selective sweeps
    \citep[e.g.][]{braverman1995hitchhiking,fay2000hitchhiking,przeworski2002signature,przeworski2005signature,schrider2015soft},
    and the impact of background selection on genetic diversity
    \citep[e.g.][]{charlesworth1993effect,charlesworth1995pattern,williamson2002genealogy,ewing2016consequences,torres2020temporal}.
    Ideally, one would like
    to have a simple, unified framework for simulating both neutral and
    non-neutral evolutionary processes, and to be able to compare the
    results of these simulations to empirical data in a manner that is
    both accessible to a wide range of researchers and highly reproducible.
    Furthermore, the framework should include the complex realities of
    genomes, including heterogeneous recombination rates,
    variation in the size and density of functional elements, and
    non-equilibrium demographic histories. Moreover, one should be able
    to model all of these features simultaneously using estimates and annotations obtained
    from a species of interest \citep[e.g.][]{schrider2020background,rodrigues2024shared}.
    %
    \stdpopsim{} provides a framework for such models,
    thus lowering the barrier to production of complex, multifaceted simulations,
    and allowing a wider range of researchers to make use of high-quality simulations
    in developing or testing their work.
    A central goal of the project is open, collaborative, and inclusive work;
    we view capacity-building across the community as equal in importance to software development.

@@

    From a user's perspective, a model of selection is specified by pairing a \texttt{DFE} object
    with a collection of genomic segments defined using an \texttt{Annotation} object.
    Multiple such pairings can be defined in one simulation
    to provide a rich model of how selection may vary along a chromosome.
    For example, coding sequences may be associated with one DFE and non-coding sequences in exons with another DFE.
    Simulations with selection are then implemented by specifying a species,
    a portion of the genome to simulate,
    a genetic map if available, a model of demography, and pairings of DFEs with genomic segments
    using either the python API or the command-line interface (Figure \ref{fig:schematic}B-C).
    Simulations with selection are generated
    using the \slim simulation engine, which is perhaps
    the most flexible simulation engine for modeling selection available to date
    (\msprime's selection models are relatively limited and thus not currently used by \stdpopsim).

@@

\section*{Discussion}
    \label{Discussion}
    In this paper, we have presented an important new addition to the \stdpopsim{} library
    that enables the simulation of genetic variation in the presence of selection.
    We have demonstrated the utility of this new API by showing how it can be used to benchmark
    the performance of different methods for demographic history inference, the inference of the distribution
    of fitness effects of new mutations, and the detection of selective sweeps.
    This allows for a wide range of models of selection to be easily simulated and compared to
    empirical data, with reproducibility, computational efficiency, and rigor.

    The exploration of performance among methods done here is not meant to be thorough
    benchmarking, but rather to highlight the utility of the \stdpopsim resource.
    Having said that, there are a number of interesting results that merit discussion.
    The first pertains to estimation of demographic history ($N_e(t)$) in the context of
    linked purifying selection. Our simulations of human and vaquita genomes
    model deleterious mutations only at exonic positions of the genome.
    As shown in Figures \ref{fig:homsap-summary-stats} and \ref{fig:vaquita-summary-stats},
    this combination only produces sizable decreases in polymorphism at exonic positions,
    which represent a small minority of sites within the genome, and does not lead to large-scale
    perturbations in genome-wide diversity. Thus, it is not surprising that estimates of $N_e(t)$
    from genome-wide data from which exons have been masked should be accurate
    (e.g., Figures \ref{fig:human-demography} and \ref{fig:vaquita-demography}).
    However, the question remains to what extent this would be true in empirical data where
    selection is not constrained to coding positions. For instance, we know
    that many genomes harbor large numbers
    of conserved non-coding elements \citep[e.g.,][]{siepel2005evolutionarily} with extremely
    strong selection acting on them \citep{katzman2007human,mclean2008dispensability}.
    We thus caution regarding extrapolation from our results. Future studies might build upon
    the annotations we used here to include selection at other portions of the genome as well
    as mixtures of DFEs across sites.

    A second important finding is that inference of the DFE
    is sensitive to the dominance of deleterious mutations.
    All three of the DFE-inference methods applied here assume that deleterious mutations act
    in an additive fashion ($h=0.5$) by default.
    However, the simulated DFE for the vaquita genome included highly recessive mutations.
    Specifically, these simulations used a DFE where mutations with $s<-0.01$ are quite recessive,
    with $h<=0.01$, and where mutations with $-0.01<s<-0.001$ have $h=0.1$.
    We found that the three DFE-inference methods underestimated $E[s]$ and overestimated the shape parameter (Figure \ref{fig:vaquita-dfe}A-B).
    This performance is not surprising since decreasing $h$ for a given distribution of $s$ will lead to a decrease in $hs$,
    or an apparent decrease in the amount of selection.
    Fitting a mis-specified DFE that assumes $h=0.5$ will then lead to underestimates of $E[s]$.
    Indeed, the distribution of $hs$ is much more accurately estimated (Figure \ref{fig:vaquita-dfe}C).
    Overall, these results are consistent with prior work showing that it is challenging to separately
    infer the DFE of $s$ along with $h$ \citep{veeramah2014evidence, kyriazis2024constraining, balick2022overcoming}
    and that a large proportion ($>5\%$) of recessive deleterious mutations can confound inferences of $s$ \citep{wade2023quantifying}.
    Given the plethora of evidence for recessive deleterious mutations
    \citep{mukai1972mutation, agrawal2011inferences, huber2018gene, di2024revisiting},
    these results suggest the need for care in DFE inference.
    Kyriazis and Lohmueller \citeyear{kyriazis2024constraining} inferred the DFE of $s$ for nonsynonymous mutations
    in humans when considering different values of $h$.
    Intriguingly, additive models showed a satisfactory fit to the SFS of nonsynonymous variants in humans,
    and more complex models of dominance did not substantially improve the fit.
    Nevertheless, models including recessive deleterious mutations, like those simulated here for the vaquita genome,
    show a similar fit to the SFS and may be more biologically realistic than fully additive models,
    given the evidence for the presence of recessive deleterious mutations.
    More broadly, new computational approaches are needed to precisely quantify the DFE and the covariance of $h$ and $s$.

    Further, inference of the DFE was done here using exon annotations of the genome in question.
    A key distinction between our analyses and those done in empirical work 
    is that we have complete knowledge of which sites are under selection in the simulation.
    Our inferences therefore represent a best case scenario. Empirical inference of the DFE is a much
    harder problem, since some mutations assumed to be free of selection
    might in reality be under selection, and the strength of selection can change over time or across environments.

    Regarding sweep detection, the inclusion of selection models into \stdpopsim allowed us to readily compare the
    effectiveness of different methods using data that reflects the demographic history, recombination rate variation,
    and genomic locations of negatively selected sites present in human populations. These results clearly demonstrate
    the impact of recombination rate variation, and underscore the importance of training methods on data with variable
    recombination rates \citep[e.g.,][]{schrider2017soft}. In addition, our results
    illustrate a strength of likelihood methods like \sweepfinder that do not require a predefined window size.
    Window-based methods, such as \diploshic, tend to lag in performance when the genomic region affected by the sweep is
    larger than the chosen window size, as can occur with very strong sweeps or low levels of
    recombination. Moreover, while all the methods examined here retain adequate power for sweep identification across
    scenarios, including the inclusion of background selection, our results underscore the importance of developing
    methods with adequate statistical power even in the face of unknown demographic histories. Indeed, larger differences
    in power were observed when applying a method to genomes simulated with different demographic histories (i.e., YRI versus CEU)
    than when calibrating a method using a null model with and without background selection.

@@

\section*{Acknowledgments}\label{acknowledgements}
We thank Tom Booker for discussions and encouragement to incorporate realistic BGS models into \stdpopsim.
We thank the numerous users of the \stdpopsim package, as well as
workshop participants who provided feedback and suggestions for improvements.
